An Overview of Distributed Version Control Systems

### 2010-07-03 laarsample.tex
Reemplazada la palabra super-set

%Arq
\subsection{Patchs}
The idea of having several clones, one for each feature or bug might be problematic. Instead, it is possible to have a single clone and then select
which of the local changes goes into the commit. Different parts of a single file can be selected to join the commit and which ones doesn't. Only those selected parts will conform the commit. The ability to select only parts of all the modifications makes the commits very atomic.

%
\subsection{Flexibility}
% Buscar reemplazo a super-set
If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository. This shows how flexible a DVCS is, to the point of being able to describe it as something that contains all  a super-set of a centralized CVS although in really it is not.

>>>>

\subsection{Patchs}
The idea of having several clones, one for each feature or bug might be problematic. Instead, it is possible to have a single clone and then select
which of the local changes goes into the commit. Different parts of a single file can be selected to join the commit and which ones doesn't. Only those selected parts will conform the commit. The ability to select only parts of all the modifications makes the commits very atomic.

\subsection{Flexibility}
If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository. This shows how flexible a DVCS is, to the point of being able to describe it as something that contains all features of a centralized CVS although in really it is not.
